Quantitative Benchmarking for Automatically Generated Conjectures

### 2017-12-01 TEBenchmarkPaper/article.tex
Remove IsaCoSy contribution
Made a bunch of notes on TEBenchmark

\begin{itemize}
\item A general methodology for benchmarking ATE systems.
\item Resolving the issue of ``interestingness'' through the use of
  theorem-proving benchmarks as a ground-truth.
\item A specific instantiation of this methodology, using the Tons of Inductive
  Problems benchmark as a corpus.
\item Automated tooling to perform this benchmarking.
\item Application of our methodology to the QuickSpec and IsaCoSy ATE systems,
  and a discussion of the results.
\end{itemize}

@@

% 1. history of terminology
Automated theory formation, the focus of this paper, derives its
terminology from psychology in which the term ``concept formation'' is
used (see, for example, \cite{bruner:67}) to describe the search for
features which differentiate exemplars from non-exemplars of various
categories. Lenat used this term in his 1977 paper: {\em Automated
  Theory Formation in Mathematics} \cite{lenat:77} and we have
extended it to describe a family of techniques used to construct and
evaluate concepts, conjectures, examples and proofs (embodied in the
HR, HRL and GC systems and derivatives, as described above).

@@

Another advantage to our statistical approach is that we can compute the
\emph{variance} of our data, which is unknown in the previous one-off
evaluations. In particular, we might be concerned that such previous evaluations
used ``popular'' theories, like those involving natural numbers, which may be
unrepresentative of typical usage: we should not expect a typical user's theory
(e.g. a software library) to be as mathematically rich as number theory!

>>>>

\begin{itemize}
\item A general methodology for benchmarking ATE systems.
\item Resolving the issue of ``interestingness'' through the use of
  theorem-proving benchmarks as a ground-truth.
\item A specific instantiation of this methodology, using the Tons of Inductive
  Problems benchmark as a corpus.
\item Automated tooling to perform this benchmarking.
\item Application of our methodology to the QuickSpec ATE system, and a
  discussion of the results.
\end{itemize}

@@

% 1. history of terminology
FIXME Automated theory formation, the focus of this paper, derives its
terminology from psychology in which the term ``concept formation'' is
used (see, for example, \cite{bruner:67}) to describe the search for
features which differentiate exemplars from non-exemplars of various
categories. Lenat used this term in his 1977 paper: {\em Automated
  Theory Formation in Mathematics} \cite{lenat:77} and we have
extended it to describe a family of techniques used to construct and
evaluate concepts, conjectures, examples and proofs (embodied in the
HR, HRL and GC systems and derivatives, as described above).

@@

Another advantage to our statistical approach is that we can compute the
\emph{spread} of our data, which is unknown in the previous one-off
evaluations. In particular, we might be concerned that such previous evaluations
used ``popular'' theories, like those involving natural numbers, which may be
unrepresentative of typical usage: we should not expect a typical user's theory
(e.g. a software library) to be as mathematically rich as number theory!
